---
title: "AI-Assisted Literature Review"
format: html
---

# Introduction

This Quarto document demonstrates an AI-assisted literature review workflow using Retrieval-Augmented Generation (RAG) and Claude 3 Opus. The workflow involves searching for relevant articles on PubMed, extracting key information, and storing it in a structured format. The AI model then queries this structured data to generate a literature review.

## the workflow of Structured Data Feeding for an AI literature review using RAG (Retrieval-Augmented Generation) and Claude 3 Opus:

# Setup

First, let's install and load the necessary libraries.

```{r}
# Install and load required libraries
install.packages(c("pubmedR", "dplyr", "readr", "stringr", "reticulate"))
library(pubmedR)
library(dplyr)
library(readr)
library(stringr)
library(reticulate)

# Load the Python environment and install necessary packages
use_python("path/to/your/python")
py_install("openai", "pandas")
```

# Data Collection and Preprocessing

Next, we'll search for relevant articles on PubMed and extract key information.

```{r}
# Define search query
query <- "your_search_query"

# Search PubMed for articles
articles <- pubmed_search(query, retmax = 100)

# Extract relevant information from articles
article_data <- articles %>%
  select(title, authors, pubdate, doi, abstract, url) %>%
  mutate(
    authors = str_c(authors, collapse = ", "),
    main_findings = str_extract(abstract, "(?i)(?<=(?:results|conclusion)).*")
  )

# Save article data to a CSV file
write_csv(article_data, "article_data.csv")
```

# AI-Assisted Literature Review

Now, we'll use RAG and Claude 3 Opus to generate the literature review.

```{python}
import anthropic
import pandas as pd

# Set up Anthropic API key
anthropic.api_key = "your_anthropic_api_key"

# Load article data from CSV file
article_data = pd.read_csv("article_data.csv")

# Function to retrieve relevant information from article data
def retrieve_info(query):
    # Perform semantic search on article data based on query
    # Return top-k most relevant articles
    pass

# Function to generate literature review using Claude 3 Opus
def generate_review(query):
    # Retrieve relevant information using RAG
    context = retrieve_info(query)
    
    # Prepare prompt for Claude 3 Opus
    prompt = f"Based on the provided context:\n\n{context}\n\nGenerate a literature review addressing the following query: {query}"
    
    # Generate literature review using Claude 3 Opus
    response = anthropic.completions.create(
        model="claude-3-opus",
        prompt=prompt,
        max_tokens=500,
        n=1,
        stop=None,
        temperature=0.7,
    )
    
    literature_review = response.generations[0].text.strip()
    return literature_review

# Generate literature review for a specific query
query = "your_literature_review_query"
literature_review = generate_review(query)
print(literature_review)
```

# Conclusion

In this Quarto document, we demonstrated an AI-assisted literature review workflow using Retrieval-Augmented Generation (RAG) and Claude 3 Opus. The workflow involved searching for relevant articles on PubMed, extracting key information, and storing it in a structured format. The AI model then queried this structured data to generate a literature review, ensuring the use of verified and accurate information.

x Note: Make sure to replace `"your_search_query"`, `"your_api_key"`, and `"your_literature_review_query"` with your actual search query, OpenAI API key, and literature review query, respectively.

This script provides a starting point for implementing the Structured Data Feeding workflow for AI-assisted literature reviews. You can further enhance and customize the script based on your specific requirements and the available AI models.



**In this updated code:**

We import the anthropic library instead of openai.
We set the anthropic.api_key to your Anthropic API key.
We use anthropic.completions.create() instead of openai.Completion.create() to generate the literature review using Claude 3 Opus.
We access the generated literature review using response.generations[0].text.strip() instead of response.choices[0].text.strip().

Please note that you need to replace "your_anthropic_api_key" with your actual Anthropic API key and "your_literature_review_query" with your specific literature review query.
Also, make sure to install the anthropic library by running pip install anthropic before running the code.
Remember to follow the guidelines and terms of service provided by Anthropic when using their API and the Claude 3 Opus model.








<!-- please apply workflow of Structured Data Feeding to design a AI literature review by using RAG and Claude 3 Opus, please write a quarto .qmd script to do so:
* Instead of giving the AI direct access to the internet, the relevant articles can be searched from PubMed, human reviewed, then preprocessed and fed to the AI in a structured format by RAG.
* This could involve extracting key information from PubMed for the articles, such as the title, authors, publication date, URL or doi, abstract, and main findings in Results and Conclusions, and storing them in a structured database in .csv format.
* The AI can then query this structured data to retrieve the relevant information for the literature review, ensuring that it only uses verified and accurate information. -->